User Preferences in Graphical and Textual Interfaces for Kubernetes

### 2021-08-23 Draft.tex
refined llui subsection

\section{Evaluation Methodology}
\subsection{Low Level User Interactions}
The video recordings were manually analyzed to count how frequently participants used the keyboard to enter a command (k), how frequently participants clicked (c), and how frequently participants moved their mouse and/or scrolled to click (m). Participant input type frequencies were stored in tuples as (k, c, m). In the terminal, we counted the total number of commands entered to determine how frequently participants used the keyboard. In the OpenShift console, we counted the number of times participants typed something followed by an enter or click to enter, as the total number of commands entered to determine how frequently participants used the keyboard. In both interfaces, we counted how frequently participants clicked by counting the number of times participants clicked to copy/paste text in the terminal and the number of times participants clicked a button in the browser. In both interfaces, mouse movements were only noted when they were followed by a click and we counted every time participants scrolled up or down the interfaces.

>>>>

\section{Evaluation Methodology}
\subsection{Low Level User Interactions}
The video recordings were manually analyzed to count how frequently participants used the keyboard to enter a command (k), how frequently participants clicked (c), and how frequently participants moved their mouse and/or scrolled to click (m). Participant input type frequencies were stored in tuples as (k, c, m). In the terminal, we counted the total number of commands entered to determine how frequently participants used the keyboard. In the OpenShift console, we counted the number of times participants typed something followed by an enter or click to enter, as the total number of commands entered to determine how frequently participants used the keyboard. In both interfaces, we counted how frequently participants clicked by counting the number of times participants clicked to copy/paste text and the number of times participants clicked a button. In both interfaces, mouse movements were only noted when they were followed by a click to copy/paste or followed by a button click and we counted every time participants scrolled up or down.
